\sysfull

### 2018-04-17 paper/systemdescription.tex
Overview figure (3) changed

\begin{wrapfigure}{t!}{0.45\textwidth}
	\centering
	\includegraphics[width=0.45\columnwidth]{figures/graffle/overview.pdf}
	\caption{\sys top-level view. \sys is composed of two core components: \emph{Task Scheduler} and \emph{Memory Manager}.}
	\label{fig:system_overview}
\end{wrapfigure}

@@

\textbf{\sys Programming and Execution Model.}  To use \sys, a programmer first writes plain, imperative C code. The programmer then must decompose the program into tasks. To manually decompose a program into tasks, the programmer designates a set of functions as tasks, sequences control-flow between these tasks, and annotates memory accesses that manipulate data shared by multiple tasks. In other words, it requires reasoning similar to prior task-based systems~\cite{chain,alpaca}.

@@

The programmer compiles their task-based code, and links to the \sys runtime,
producing a \sys-enabled binary. The \sys runtime implements \sys's task-based
programming and execution model. The runtime system also includes \sys's novel
{\em virtualizing memory manager} and its {\em adaptive task scheduler}, both
of which are essential to \sys's adaptive task-based execution.

\textbf{\sys Adaptive Task Scheduler.} 
\sys's adaptive task scheduler decides when to coalesce consecutive tasks
together to amortize commit and transition costs, and when to downscale a task,
breaking it into multiple tasks, to avoid non-termination.

@@

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager. \sys's memory manager
paginates memory and ensures that data in a page remain consistent despite
power interruptions. \sys allows a task to manipulate data in a volatile copy
of a page only. Pages swap between volatile and non-volatile memory, depending
on the capacity of the volatile memory and the program's access pattern. \sys
tracks a task's memory accesses efficiently at page granularity (rather than
using, e.g., costly word-granular tracking). When a task ends, each page it
accessed commits from volatile memory (or from a non-volatile swap region for
dirty pages) back to the non-volatile main memory. Pages efficiently,
atomically commit using a two-phase commit procedure accelerated using hardware
support for direct memory access (DMA). Section~\ref{sec:memory_virtulaization}
provides details of \sys's memory manager.

>>>>

\begin{wrapfigure}{t!}{0.45\textwidth}
	\centering
	\includegraphics[width=0.45\columnwidth]{figures/overview.pdf}
	\caption{System's top-level view. \sys is composed of two core components: \emph{Adaptive Task Scheduler} and \emph{Virtual Memory Manager}.}
	\label{fig:system_overview}
\end{wrapfigure}

@@

\textbf{Programming and Execution Model.}  To use \sys, a programmer first writes plain, imperative C code. The programmer then must decompose the program into tasks. To manually decompose a program into tasks, the programmer designates a set of functions as tasks, sequences control-flow between these tasks, and annotates memory accesses that manipulate data shared by multiple tasks. In other words, it requires reasoning similar to prior task-based systems~\cite{chain,alpaca}.

@@

The programmer compiles their task-based code, and links to \sys runtime,
producing a \sys-enabled binary. The runtime implements \sys's task-based
programming and execution model. The runtime system also includes \sys's novel
{\em virtual memory manager} and its {\em adaptive task scheduler}, both
of which are essential to \sys's adaptive task-based execution.

\textbf{Adaptive Task Scheduler.} 
\sys's adaptive task scheduler decides when to coalesce consecutive tasks
together to amortize commit and transition costs, and when to downscale a task,
breaking it into multiple tasks, to avoid non-termination.

@@

\textbf{Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager. \sys's memory manager
paginates memory and ensures that data in a page remain consistent despite
power interruptions. \sys allows a task to manipulate data in a volatile copy
of a page only. Pages swap between volatile and non-volatile memory, depending
on the capacity of the volatile memory and the program's access pattern. \sys
tracks a task's memory accesses efficiently at page granularity (rather than
using, e.g., costly word-granular tracking). When a task ends, each page it
accessed commits from volatile memory (or from a non-volatile swap region for
dirty pages) back to the non-volatile main memory. Pages efficiently,
atomically commit using a two-phase commit procedure accelerated using hardware
support for direct memory access (DMA). Section~\ref{sec:memory_virtulaization}
provides details of \sys's memory manager.
